### 2016-09-07 notions.tex
no message

First, a set~$S$ is chosen according to some
distribution~$\distr{}{}$ over the collection of multisets
$\mathcal{S}$ associated with~$\Pi$, and then
$\Rep(S)$ is run to generate $(\pubaux,\privaux)$. \jnote{I thought we were going to let
the adversary choose~$S$?}
%(Unless stated otherwise, we assume security holds for all distributions and thus for all sets $S$.)
Adversary~$A$ is given~$\pubaux$~as input; it is also
provided with access to an oracle~$\TestOracle$ that, on input a query~$q \in \calQ$,
returns $\Qry(\pubaux,\privaux,q)$ and increments
a counter if this result is in error.  The adversary wins if it
manages to cause at least~$r>0$ such errors among its queries.
\jnote{If we are specializing the set-multiplicity data structures then we
may as well have the attacker query $x$ which gets translated to query $q_x$. If
we are trying to be more general then we should be consistent.} \jnote{Why does $A$ output
anything at all?}

@@

\begin{figure}[htp]
\centering
\fpage{.6}{
\hpagess{.5}{.45}
{
\experimentv{$\ExpCorrect{\setprim,\distr{}{},r}{A}$}\\
$S \getsr \distr{}{}$\\
$\mathrm{err}\gets 0$\\
$(\pubaux,\privaux) \getsr \Rep(S)$\\
$z \getsr A^{\TestOracle}(S,\pubaux)$\\
if $\mathrm{err} < r$ then Return 0\\
Return 1
}
%
{
\oracle{$\TestOracle(q)$}\\
$a \gets \Qry(\pubaux,\privaux,q)$\\
if $a \neq q(S)$ then \\
\nudge $\mathrm{err}\gets\mathrm{err}+1$\\
Return~$(a,\mathrm{err})$
}
}
\caption{Correctness of~$\Pi$ against an (adaptive) adversary~$A$, when
  the represented multiset~$S$ is sampled according to distribution~$\distr{}{}$.}
\label{fig:correctness}
\end{figure}

In this experiment we track the time complexity (relative to some
model of computation) and query complexity (i.e., number of
queries to $\TestOracle$) of~$A$.
We define the advantage of adversary~$A$ in the correctness experiment as
$\AdvCorrect{\Pi,\distr{}{},r}{A} = \Prob{\ExpCorrect{\Pi,\distr{}{}, r,}{A}=1}$.
Overloading notation, we write $\AdvCorrect{\Pi,\distr{}{},r}{t,q}$ for the maximum over
all~$t$-time adversaries that ask at most~$q$ queries. We say that a
set-representation data structure~$\Pi$ is $(t,q,r,\epsilon')$-correct if $\AdvCorrect{\Pi,\distr{}{},r}{t,q} \leq \epsilon'$.
\jnote{Note~$q$ is overloaded here.}
%\jnote{Note that test includes err because we don't want to penalize
%the adversary's resources for computing $q(S)$.}

\heading{Comparison to Naor-Yogev definition.}
The style of the Naor-Yogev definition is different from ours.
Lifting their definition\footnote{They focus specifically on set-representation data structures
with no false negatives, and consider worst-case choice of~$S$. Their data-structure syntax
also does not distinguish public and private portions of the representation. Nevertheless, it is straightforward
to extend their definition to more closely match ours.}
to our setting,
the experiment is similar but the attacker
succeeds only if it outputs a (single) query $q$ for which
$\Qry(\pubaux,\privaux, q) \neq q(S)$  \emph{subject to the restriction that it did not
previously query $q$ to its $\TestOracle$ oracle} (see Figure~\ref{fig:NYcorrectness}).

\begin{figure}[htp]
\centering
\fpage{.6}{
\hpagess{.5}{.45}
{
\experimentv{$\ExpCorrect{\setprim,\distr{}{},r}{A}$}\\
$S \getsr \distr{}{}$\\
$\mathcal{Q} \gets \emptyset$\\
%$\mathrm{err}\gets 0$\\
$(\pubaux,\privaux) \getsr \Rep(S)$\\
$q \getsr A^{\TestOracle}(S,\pubaux)$\\
if $\left(q \not \in \mathcal{Q}\right.$ and \\
\nudge $\left.\Qry(\pubaux,\privaux,q) \neq q(S)\right)$ \\
\nudge \nudge then Return 1\\
Return 0
}
%
{
\oracle{$\TestOracle(q)$}\\
$a \gets \Qry(\pubaux,\privaux,q)$\\
$\mathcal{Q} \gets \mathcal{Q} \cup \{q\}$ \\
%\nudge $\mathrm{err}\gets\mathrm{err}+1$\\
Return~$(a,q(S))$
}
}
\caption{The Naor-Yogev definition of
correctness, adapted to our setting.}
\label{fig:NYcorrectness}
\end{figure}

It will be interesting to understand formally the relation between our
definition and theirs.
Here are some observations:
\begin{enumerate}
\item Say a scheme is $\epsilon_{NY}$-secure under the NY definition.
Then we claim it is $(t,q, r, q\epsilon_{NY}/r)$-correct. To see
this, assume not. Then there is a $t$-time attacker~$A$ that, with
probability at least $\epsilon'=q\epsilon_{NY}/r$,
issues~$q$ Test-queries of which at least~$r$ cause errors. If we simply run~$A$ and then choose a random Test-query to
output, we succeed with probability at least $\epsilon' \cdot r/q$. It is unclear whether this is tight.

>>>>

First, a set~$S$ is chosen according to some
distribution~$\distr{}{}$ over the collection of multisets
$\mathcal{S}$ associated with~$\Pi$, and then
$\Rep(S)$ is run to generate $(\pubaux,\privaux)$. \jnote{I thought we were going to let
the adversary choose~$S$?} \jnote{If instead we choose $S$ from ${\cal D}$, then
is it clear we want to give $S$ to~$A$?}
%(Unless stated otherwise, we assume security holds for all distributions and thus for all sets $S$.)
Adversary~$A$ is given~$\pubaux$~as input; it is also
provided with access to an oracle~$\TestOracle$ that, on input a query~$q \in \calQ$,
returns $\Qry(\pubaux,\privaux,q)$ and increments
a counter if this result is in error.  The adversary wins if it
manages to cause at least~$r>0$ such errors among its queries.
\jnote{If we are specializing the set-multiplicity data structures then we
may as well have the attacker query $x$ which gets translated to query $q_x$. If
we are trying to be more general then we should be consistent.} \jnote{Why does $A$ output
anything at all?}

@@

\jnote{I changed $\TestOracle$ so that it outputs $(a, q(S))$ rather
than $(a,\mathrm{err})$. Note that the latter can be computed from the former,
and in the general case I think the former is what we want.} \jnote{I also changed
the definition so the adversary has to find $r$ {\bf unique} inputs on which
there is an error.}

\begin{figure}[htp]
\centering
\fpage{.65}{
\hpagess{.5}{.45}
{
\experimentv{$\ExpCorrect{\setprim,\distr{}{},r}{A}$}\\
$S \getsr \distr{}{}$\\
$\mathcal{Q} \gets \emptyset$ \\
$\mathrm{err}\gets 0$\\
$(\pubaux,\privaux) \getsr \Rep(S)$\\
$z \getsr A^{\TestOracle}(S,\pubaux)$\\
if $\mathrm{err} < r$ then Return 0\\
Return 1
}
%
{
\oracle{$\TestOracle(q)$}\\
$a \gets \Qry(\pubaux,\privaux,q)$\\
if ($a \neq q(S)$ and $q \not \in \mathcal{Q}$) then \\
\nudge $\mathrm{err}\gets\mathrm{err}+1$\\
$\mathcal{Q} \gets \mathcal{Q} \cup \{q\}$ \\
Return~$(a,q(S))$
}
}
\caption{Correctness of~$\Pi$ against an (adaptive) adversary~$A$, when
  the represented multiset~$S$ is sampled according to distribution~$\distr{}{}$.}
\label{fig:correctness}
\end{figure}

In this experiment we track the time complexity (relative to some
model of computation) and query complexity (i.e., number of
queries to $\TestOracle$) of~$A$.
We define the advantage of adversary~$A$ in the correctness experiment as
$\AdvCorrect{\Pi,\distr{}{},r}{A} = \Prob{\ExpCorrect{\Pi,\distr{}{}, r}{A}=1}$.
Overloading notation, we write $\AdvCorrect{\Pi,\distr{}{},r}{t,q}$ for the maximum over
all~$t$-time adversaries that ask at most~$q$ queries. We say that a
set-representation data structure~$\Pi$ is $(t,q,r,\epsilon')$-correct if $\AdvCorrect{\Pi,\distr{}{},r}{t,q} \leq \epsilon'$.
\jnote{Note~$q$ is overloaded here.}
%\jnote{Note that test includes err because we don't want to penalize
%the adversary's resources for computing $q(S)$.}

\heading{Comparison to the Naor-Yogev definition.}
The structure of the Naor-Yogev definition is different from ours.
Lifting their definition\footnote{They focus specifically on set-representation data structures
with no false negatives, and consider worst-case choice of~$S$. Their data-structure syntax
also does not distinguish public and private portions of the representation. Nevertheless, it is straightforward
to extend their definition to more closely match ours.}
to our setting,
the experiment is similar but the attacker
succeeds only if it outputs a (single) query $q$ for which
$\Qry(\pubaux,\privaux, q) \neq q(S)$  \emph{subject to the restriction that it did not
previously query $q$ to its $\TestOracle$ oracle}. We refer to
Figure~\ref{fig:NYcorrectness} for a definition of the relevant experiment.
We define the advantage of adversary~$A$ as
$\NYAdvCorrect{\Pi,\distr{}{}}{A} = \Prob{\NYExpCorrect{\Pi,\distr{}{}}{A}=1}$,
and write $\NYAdvCorrect{\Pi,\distr{}{},r}{t,q}$ for the maximum over
all~$t$-time adversaries that ask at most~$q$ queries. We say that a
set-representation data structure~$\Pi$ is $(t,q,\epsilon')$-NY-correct if
$\NYAdvCorrect{\Pi,\distr{}{}}{t,q} \leq \epsilon'$. \jnote{This should all probably
move to an appendix; it's a lot of notation to digest for something we never use again
in the paper.}

\jnote{Just noticed something (else) odd about the NY definition: we cannot assume w.l.o.g.\
that $A$ makes exactly $q$ queries, and in fact it is possible to have cases where increasing
the number of queries the attacker makes can decrease its advantage! This seems like
another drawback of the definition.}

\begin{figure}[htp]
\centering
\fpage{.6}{
\hpagess{.5}{.45}
{
\experimentv{$\ExpCorrect{\setprim,\distr{}{}}{A}$}\\
$S \getsr \distr{}{}$\\
$\mathcal{Q} \gets \emptyset$\\
%$\mathrm{err}\gets 0$\\
$(\pubaux,\privaux) \getsr \Rep(S)$\\
$q \getsr A^{\TestOracle}(S,\pubaux)$\\
if $\left(q \not \in \mathcal{Q}\right.$ and \\
\nudge $\left.\Qry(\pubaux,\privaux,q) \neq q(S)\right)$ \\
\nudge \nudge then Return 1\\
Return 0
}
%
{
\oracle{$\TestOracle(q)$}\\
$a \gets \Qry(\pubaux,\privaux,q)$\\
$\mathcal{Q} \gets \mathcal{Q} \cup \{q\}$ \\
%\nudge $\mathrm{err}\gets\mathrm{err}+1$\\
Return~$(a,q(S))$
}
}
\caption{The Naor-Yogev definition of
correctness, adapted to our setting.}
\label{fig:NYcorrectness}
\end{figure}

With the above in place we can now relate their definition to ours.

\jnote{There's something ``morally wrong'' with the follow theorem statement:
if we increase $q$ then the assumption about the NY-correctness of $\Pi$ (presumably)
gets stronger---even if formally that is not true---but the conclusion of the theorem
becomes weaker.}

\begin{theorem}
If $\Pi$ is $(t,q,\epsilon')$-NY-correct, then it is also
$(t, q', r, q'\epsilon'/r)$-correct for any $q' \leq q+1$ and $r\geq 1$.
\end{theorem}
\begin{proof}
Let $\Pi$ be a set-representation data structure that is $(t,q,\epsilon')$-NY-correct,
and assume that for some $q' \leq q+1$ and $r \geq 1$
there is an adversary $A$ running in time~$t$
and making $q'$ oracle queries (note that without loss of generality
we may assume $A$ always makes exactly $q'$ queries) such that
$\AdvCorrect{\Pi,\distr{}{},r}{A} > q'\epsilon'/r$.
With probability at least
$q'\epsilon'/r$ in an execution of $\ExpCorrect{\Pi,\distr{}{},r}{A}$, we have that
$A$ makes at least $r$ distinct queries to $\TestOracle$ for which
an incorrect answer is returned. Let $A'$ be the algorithm that simply
runs~$A$, but chooses
uniformly one of the $q'$ queries of $A$ to its $\TestOracle$ oracle and outputs that query
as its final output. Then with probability at least $r/q' \cdot (q'\epsilon'/r)=\epsilon'$
the query chosen by $A'$
leads to an incorrect answer, and was not previously asked to the $\TestOracle$ oracle.
Since the running time of $A'$ is at most $t$, and it makes at most $q'-1 \leq q$ queries
to its oracle, this is a contradiction.
\end{proof}

\jnote{It is unclear whether the above is tight, but it is also unclear whether
that is something worth thinking about. }

\begin{enumerate}
\item Say a scheme is $\epsilon_{NY}$-secure under the NY definition.
Then we claim it is $(t,q, r, q\epsilon_{NY}/r)$-correct. To see
this, assume not. Then there is a $t$-time attacker~$A$ that, with
probability at least $\epsilon'=q\epsilon_{NY}/r$,
issues~$q$ Test-queries of which at least~$r$ cause errors.
If we simply run~$A$ and then choose a random Test-query to
output, we succeed with probability at least $\epsilon' \cdot r/q$.
It is unclear whether this is tight.
